My title

### 2024-11-29 paper/paper.qmd
Updated model predictors and paper

---
title: "My title"
subtitle: "An analysis of solved and unsolved homicides from 2007 to 2017 in the United States's 47 largest cities"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
library(ggplot2)
library(modelsummary)
library(rstanarm)
```

@@

## Model Results {#sec-model-results}

@@

@@

>>>>

---
title: "My title"
subtitle: "An analysis of solved and unsolved homicides from 2007 to 2017 in the United States's 2 largest cities"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
library(ggplot2)
library(modelsummary)
library(rstanarm)

# Read in analysis data
analysis_data_homicides <- 
  read_parquet("../data/02-analysis_data/cleaned_data_homicides.parquet")
# Read in model data
unsolved_model_results <- readRDS("../models/unsolved_homicide_model.rds")
```

@@

## Model Results {#sec-model-results}
```{r}
#| label: tbl-model-result
#| tbl-cap: Relationship between a homicide being unsolved from 2007 to 2017 with the city and date (month, year) a victim is found in/on and the race, age, and sex of a victim with their mean absolute deviation (MAD) values in parenthesis    
#| echo: false
#| warning: false
#| message: false

modelsummary(
  # List out unsolved_model_results information
  list("Unsolved homicides (2007 to 2017)" = unsolved_model_results),
  # Specify MAD as the statistic
  statistic = "mad"
)
```

```{r}
#| label: fig-model-result-ci
#| fig-cap: The credible intervals (line) for coefficient estimates (dot) of predictors of homicides that go unsolved from 2007 to 2017
#| echo: false
#| warning: false
#| message: false
# Specify credible interval to be 90% and present model results
modelplot(unsolved_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credible interval")
```

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(unsolved_model_results) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(unsolved_model_results) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(unsolved_model_results, "trace")

plot(unsolved_model_results, "rhat")
```
